Fixing Vulnerabilities Hinders Maintainability

### 2019-02-01 paper/ICPC19/icpc19.tex
fixing

In this study, our concern is to study whether while improving software
security, developers are also inserting a negative impact on the maintainability
of their software which may increase technical debt when choosing the easiest
solution instead of the using the best approach. To answer the following two
research questions, we use a dataset of security refactorings to measure the
impact of the changes in the maintainability of open-source software.

>>>>

In this paper, our concern is to study whether, while improving software
security, developers are also negatively impacting the maintainability
of their software application. To answer the following two
research questions, we use a dataset of security refactorings to measure the
impact of the changes in the maintainability of open-source software.
